Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
Avoid footnote.

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all built-in
estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible
\textit{out-of-box} for non-experts. Finally, the constructor of an estimator
never performs any actual learning, nor does it even see any training dataset.
Its only goal is to set the parameter values and freeze the behavior of the
estimator.

The estimator interface defines a \texttt{fit} method. This method is called
with training data (e.g., supplied as two arrays \texttt{X\_train} and
\texttt{y\_train} in supervised learning estimators). Its task is to run a
learning algorithm and to determine model- specific parameters from the training
data and set these as attributes on the estimator object. As a convention, the
parameters learned by an estimator are exposed as public
attributes\footnote{Note that the learned parameters are different from the
hyper-parameters given to the constructor. To distinguish between the two,
learned parameters are all suffixed with a trailing underscore (e.g.,
\texttt{clf.coef\_} in the case of linear models is the vector of
coefficients learned from the data).} on the trained object.

>>>>

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all built-in
estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible
\textit{out-of-box} for non-experts. Finally, the constructor of an estimator
never performs any actual learning (this is the role of the \texttt{fit} method,
see below).  Its only goal is to set the parameter values and freeze the
behavior of the estimator.

The estimator interface defines a \texttt{fit} method. This method is called
with training data (e.g., supplied as two arrays \texttt{X\_train} and
\texttt{y\_train} in supervised learning estimators). Its task is to run a
learning algorithm and to determine model- specific parameters from the training
data and set these as attributes on the estimator object. As a convention, the
parameters learned by an estimator are exposed as public attributes whose name
is suffixed with a trailing underscore (e.g., \texttt{coef\_} for the
learned coefficients of a linear model).

on the trained object.
